\thetitle

### 2021-05-07 paper/paper.tex
update

\paragraph{Medium Variability.} The results for medium variability in the system are presented in
Table~\ref{tbl:unif}, where a uniform demand interarrival time is used. We use the tuples
\(70-\Unif\), \(80-\Unif\), and \(90-\Unif\) to indicate the experimental setup of using uniform
demand interarrival times with a aimed bottleneck utilisation of \(70\%\), \(80\%\), or \(90\%\)
respectively. The results state the accumulated costs, averaged over all replications, for the work
in process (WIPC), the finished goods inventory (FGIC), the backorder costs (BOC), as well as the
sum of the finished good inventory and backorder costs (FGIC+BOC) and the sum over all three cost
centers (SUM). For a better insight in the timing performance we also provide the average shopfloor
throughput time (SFTT), i.e.\@ the average time an order spends in the system after being released
and until reaching the finished goods inventory, the finished goods inventory time (FGIT), as well
as the service level (SL). The later is given in percentage and states the percentage of orders that
were produced on time. Finally, the actual measured costs per period (Cost.p.P) and the by the
algorithm learned average reward \(\avgrew\) are stated. The tested methods are the deep Q-Learning
algorithm with discount factor \(0.99\) (\(\ql{0.99}\)), the \ARA{} algorithm with discount factors
\(0.99\) (\(\rl{0.99}\)) and \(1.00\) (\(\rl{1.00}\)), as well as the backward infinite loading
technique \BIL{} with fixed lead times between \(1\) and \(4\) as indicated by the number
($\BILOne$-$\BILFour$).

For the case of medium variability with a utilisation of \(70\%\) we can see that

@@

    \begin{tabular}{crrrccccccc}

@@

      % 70-\(\Unif\) & WIPC              & FGIC              & BOC                & FGIC+BOC                        & SUM                & SFTT          & FGIT                & SL(\%)       & Cost.p.P             & \(\avgrew^{\pol}\) \\
      % \midrule
      % \ql{0.99}    & \cost{38776.300}  & \cost{133872.800} & \cost{82673.600 }  &                                 & \cost{255322.700}  & \timem{1.340} & \timem{2.558}       & \tard{0.095} &                      &                    \\
      % \rl{0.99}    & \cost{37111.000}  & \cost{113425.600} & \cost{98654.400 }  &                                 & \cost{249191.000}  & \timem{1.305} & \timem{2.412}       & \tard{0.110} &                      &                    \\
      % \rl{1.00}    & \cost{38755.000}  & \cost{156444.000} & \cost{59718.400 }  &                                 & \cost{254917.400}  & \timem{1.339} & \timem{2.679}       & \tard{0.068} &                      &                    \\
      % \BILOne{}    & \cost{32159.900}  & \cost{     0.000} & \cost{514558.400}  &                                 & \cost{546718.300}  & \timem{1.202} & \timem{1.693}       & \tard{0.552} &                      &                    \\
      % \BILTwo{}    & \cost{32169.900}  & \cost{ 83391.200} & \cost{106219.200}  &                                 & \cost{221780.300}  & \timem{1.202} & \timem{2.143}       & \tard{0.114} &                      &                    \\
      % \BILThree{}  & \cost{32239.800}  & \cost{247416.800} & \cost{21382.400 }  &                                 & \cost{301039.000}  & \timem{1.204} & \timem{3.029}       & \tard{0.022} &                      &                    \\
      % \BILFour{}   & \cost{32262.600}  & \cost{428865.200} & \cost{5483.200  }  &                                 & \cost{466611.000}  & \timem{1.204} & \timem{4.007}       & \tard{0.006} &                      &                    \\

@@

      70-\(\Unif\)   & WIPC              & FGIC              & BOC                & FGIC+BOC                        & SUM                & SFTT          & FGIT                & SL(\%)       & Cost.p.P             & \(\avgrew^{\pol}\) \\

@@

      \ql{0.99}      & \cost{38563.000}  & \cost{134703.600} & \cost{81704.800}   & \fgiboc{134703.600}{81704.800}  & \cost{254971.400}$^{1}$  & \timem{1.335} & \fgit{1.335}{2.558} & \tard{0.094} & \costpp{254971.400}  &                    \\
      \rl{0.99}      & \cost{37197.750}  & \cost{113100.800} & \cost{100398.400}  & \fgiboc{113100.800}{100398.400} & \cost{250696.950}  & \timem{1.307} & \fgit{1.307}{2.412} & \tard{0.111} & \costpp{250696.950}  & \rnd{35.040}       \\
      \rl{1.00}      & \cost{38659.100}  & \cost{156659.200} & \cost{59743.200}   & \fgiboc{156659.200}{59743.200}  & \cost{255061.500}$^{1}$  & \timem{1.338} & \fgit{1.338}{2.678} & \tard{0.068} & \costpp{255061.500}  & \rnd{36.501}       \\
      \BILOne{}      & \cost{32056.500}  & \cost{0.000}      & \cost{512904.000}  & \fgiboc{0.000}{512904.000}      & \cost{544960.500}  & \timem{1.200} & \fgit{1.200}{1.691} & \tard{0.551} & \costpp{544960.500}  &                    \\
      \BILTwo{}      & \cost{32063.850}  & \cost{83461.000}  & \cost{105009.600}  & \fgiboc{83461.000}{105009.600}  & \textbf{\cost{220534.450}}  & \timem{1.200} & \fgit{1.200}{2.142} & \tard{0.114} & \textbf{\costpp{220534.450}}  &                    \\
      \BILThree{}    & \cost{32155.150}  & \cost{247727.000} & \cost{21680.800 }  & \fgiboc{247727.000}{21680.800 } & \cost{301562.950}  & \timem{1.202} & \fgit{1.202}{3.029} & \tard{0.022} & \costpp{301562.950}  &                    \\
      \BILFour{}     & \cost{32140.550}  & \cost{429097.800} & \cost{5076.800 }   & \fgiboc{429097.800}{5076.800 }  & \cost{466315.150}  & \timem{1.202} & \fgit{1.202}{4.007} & \tard{0.005} & \costpp{466315.150}  &                    \\

@@

      80-\(\Unif\)   & WIPC              & FGIC              & BOC                & FGIC+BOC                        & SUM                & SFTT          & FGIT                & SL(\%)       & CostpP               & \(\avgrew^{\pol}\) \\

@@

      \ql{0.99}      & \cost{63095.100}  & \cost{180403.800} & \cost{121528.000}  & \fgiboc{180403.800}{121528.000} & \textbf{\cost{365026.900}}  & \timem{1.680} & \fgit{1.680}{3.019} & \tard{0.103} & \textbf{\costpp{365026.900}} &                    \\
      \rl{0.99}      & \cost{65310.650}  & \cost{168489.200} & \cost{148593.600}  & \fgiboc{168489.200}{148593.600} & \cost{382393.450}  & \timem{1.721} & \fgit{1.721}{3.005} & \tard{0.136} & \costpp{382393.450}  & \rnd{52.918}       \\
      \rl{1.00}      & \cost{60778.500}  & \cost{234045.000} & \cost{76168.000}   & \fgiboc{234045.000}{76168.000}  & \cost{370991.500}$^{1}$  & \timem{1.637} & \fgit{1.637}{3.226} & \tard{0.066} & \costpp{370991.500}  & \rnd{52.291}       \\
      \BILOne{}      & \cost{51888.650}  & \cost{0.000}      & \cost{830218.400}  & \fgiboc{0.000}{830218.400}      & \cost{882107.050}  & \timem{1.474} & \fgit{1.474}{1.968} & \tard{0.672} & \costpp{882107.050}  &                    \\
      \BILTwo{}      & \cost{51998.950}  & \cost{70108.800}  & \cost{255166.400}  & \fgiboc{70108.800}{255166.400}  & \cost{377274.150}  & \timem{1.476} & \fgit{1.476}{2.298} & \tard{0.206} & \costpp{377274.150}  &                    \\
      \BILThree{}    & \cost{51976.550}  & \cost{240175.000} & \cost{77822.400}   & \fgiboc{240175.000}{77822.400}  & \cost{369973.950}$^{1}$  & \timem{1.475} & \fgit{1.475}{3.091} & \tard{0.060} & \costpp{369973.950}  &                    \\
      \BILFour{}     & \cost{51827.050}  & \cost{442307.600} & \cost{26711.200}   & \fgiboc{442307.600}{26711.200}  & \cost{520845.850}  & \timem{1.472} & \fgit{1.472}{4.031} & \tard{0.019} & \costpp{520845.850}  &                    \\

@@

      90-\(\Unif\)   & WIPC              & FGIC              & BOC                & FGIC+BOC                        & SUM                & SFTT          & FGIT                & SL(\%)       & CostpP               & \(\avgrew^{\pol}\) \\

@@

      \ql{0.99}      & \cost{98909.150}  & \cost{190681.000} & \cost{297333.600}  & \fgiboc{190681.000}{297333.600} & \cost{586923.750}$^{1}$  & \timem{2.133} & \fgit{2.133}{3.417} & \tard{0.173} & \costpp{586923.750}  &                    \\
      \rl{0.99}      & \cost{105348.200} & \cost{263950.600} & \cost{207183.200}  & \fgiboc{263950.600}{207183.200} & \textbf{\cost{576482.000}}$^{1}$  & \timem{2.238} & \fgit{2.238}{3.825} & \tard{0.121} & \textbf{\costpp{576482.000}}  & \rnd{79.826}       \\
      \rl{1.00}      & \cost{107873.800} & \cost{240798.800} & \cost{253865.600}  & \fgiboc{240798.800}{253865.600} & \cost{602538.200}$^{2}$  & \timem{2.280} & \fgit{2.280}{3.771} & \tard{0.153} & \costpp{602538.200}  & \rnd{80.425}       \\
      \BILOne{}      & \cost{88658.100}  & \cost{0.000}      & \cost{1418529.600} & \fgiboc{0.000}{1418529.600}     & \cost{1507187.700} & \timem{1.964} & \fgit{1.964}{2.462} & \tard{0.790} & \costpp{1507187.700} &                    \\
      \BILTwo{}      & \cost{88317.700}  & \cost{50854.400}  & \cost{646000.800}  & \fgiboc{50854.400}{646000.800}  & \cost{785172.900}  & \timem{1.958} & \fgit{1.958}{2.666} & \tard{0.355} & \costpp{785172.900}  &                    \\
      \BILThree{}    & \cost{88252.450}  & \cost{207210.600} & \cost{299885.600}  & \fgiboc{207210.600}{299885.600} & \cost{595348.650}$^{2}$  & \timem{1.957} & \fgit{1.957}{3.309} & \tard{0.148} & \costpp{595348.650}  &                    \\
      \BILFour{}     & \cost{87774.600}  & \cost{415178.200} & \cost{153612.800}  & \fgiboc{415178.200}{153612.800} & \cost{656565.600}  & \timem{1.950} & \fgit{1.950}{4.158} & \tard{0.071} & \costpp{656565.600}  &                    \\

@@

    not sign.\@ different to each other.}

@@

@@

@@

      70-\(\Exp\) & WIPC              & FGIC              & BOC               & FGIC+BOC                        & SUM                              & SFTT          & FGIT                & SL(\%)       & Cost.p.P                     & \(\avgrew^{\pol}\) \\

@@

      \ql{0.99}   & \cost{53873.500}  & \cost{142398.800} & \cost{164427.200} & \fgiboc{142398.800}{164427.200} & \cost{360699.500}$^{1}$          & \timem{1.585} & \fgit{1.585}{2.796} & \tard{0.162} & \costpp{360699.500}          &                    \\
      \rl{0.99}   & \cost{61419.850}  & \cost{181702.200} & \cost{115287.200} & \fgiboc{181702.200}{115287.200} & \cost{358409.250}                & \timem{1.734} & \fgit{1.734}{3.145} & \tard{0.107} & \costpp{358409.250}          & \rnd{50.787}       \\
      \rl{1.00}   & \cost{56578.800}  & \cost{199310.000} & \cost{115714.400} & \fgiboc{199310.000}{115714.400} & \cost{371603.200}                & \timem{1.639} & \fgit{1.639}{3.136} & \tard{0.113} & \costpp{371603.200}          & \rnd{50.575}       \\
      \BILOne{}   & \cost{48547.100}  & \cost{     0.000} & \cost{776753.600} & \fgiboc{     0.000}{776753.600} & \cost{825300.700}                & \timem{1.479} & \fgit{1.479}{1.975} & \tard{0.663} & \costpp{825300.700}          &                    \\
      \BILTwo{}   & \cost{48618.850}  & \cost{ 66927.200} & \cost{248638.400} & \fgiboc{ 66927.200}{248638.400} & \cost{364184.450}$^{1}$          & \timem{1.480} & \fgit{1.480}{2.312} & \tard{0.220} & \costpp{364184.450}          &                    \\
      \BILThree{} & \cost{48632.050}  & \cost{222603.200} & \cost{ 74568.800} & \fgiboc{222603.200}{ 74568.800} & \textbf{\cost{345804.050}}       & \timem{1.481} & \fgit{1.481}{3.094} & \tard{0.063} & \textbf{\costpp{345804.050}} &                    \\
      \BILFour{}  & \cost{48514.200}  & \cost{409531.200} & \cost{ 23406.400} & \fgiboc{409531.200}{ 23406.400} & \cost{481451.800}                & \timem{1.478} & \fgit{1.478}{4.029} & \tard{0.019} & \costpp{481451.800}          &                    \\

@@

      80-\(\Exp\) & WIPC              & FGIC              & BOC               & FGIC+BOC                        & SUM                              & SFTT          & FGIT                & SL(\%)       & Cost.p.P                     & \(\avgrew^{\pol}\) \\

@@

      \ql{0.99}   & \cost{87706.700}  & \cost{227485.400} & \cost{225150.400} & \fgiboc{227485.400}{225150.400} & \cost{540342.500}$^{1}$          & \timem{2.043} & \fgit{2.043}{3.541} & \tard{0.166} & \costpp{540342.500}          &                    \\
      \rl{0.99}   & \cost{89838.950}  & \cost{253476.000} & \cost{185687.200} & \fgiboc{253476.000}{185687.200} & \cost{529002.150}$^{1,2}$        & \timem{2.078} & \fgit{2.078}{3.689} & \tard{0.124} & \costpp{529002.150}          & \rnd{70.527}       \\
      \rl{1.00}   & \cost{87171.500}  & \cost{242915.600} & \cost{198456.000} & \fgiboc{242915.600}{198456.000} & \cost{528543.100}$^{2,3}$        & \timem{2.034} & \fgit{2.034}{3.599} & \tard{0.134} & \costpp{528543.100}          & \rnd{72.944}       \\
      \BILOne{}   & \cost{78731.850}  & \cost{     0.000} & \cost{1259709.60} & \fgiboc{     0.000}{1259709.60} & \cost{1338441.45}                & \timem{1.884} & \fgit{1.884}{2.382} & \tard{0.771} & \costpp{1338441.450}         &                    \\
      \BILTwo{}   & \cost{78203.150}  & \cost{ 52303.200} & \cost{548736.000} & \fgiboc{ 52303.200}{548736.000} & \cost{679242.350}                & \timem{1.875} & \fgit{1.875}{2.602} & \tard{0.350} & \costpp{679242.350}          &                    \\
      \BILThree{} & \cost{79029.850}  & \cost{200273.200} & \cost{242100.800} & \fgiboc{200273.200}{242100.800} & \textbf{\cost{521403.850}}$^{3}$ & \timem{1.890} & \fgit{1.890}{3.265} & \tard{0.142} & \textbf{\costpp{521403.850}} &                    \\
      \BILFour{}  & \cost{79384.750}  & \cost{395493.000} & \cost{116943.200} & \fgiboc{395493.000}{116943.200} & \cost{591820.950}                & \timem{1.896} & \fgit{1.896}{4.128} & \tard{0.062} & \costpp{591820.950}          &                    \\

@@

      90-\(\Exp\) & WIPC              & FGIC              & BOC               & FGIC+BOC                        & SUM                              & SFTT          & FGIT                & SL(\%)       & Cost.p.P                     & \(\avgrew^{\pol}\) \\

@@

      \ql{0.99}   & \cost{168655.950} & \cost{222145.800} & \cost{788662.400} & \fgiboc{222145.800}{788662.400} & \cost{1179464.150}$^{1}$               & \timem{3.134} & \fgit{3.134}{4.501} & \tard{0.285} & \costpp{1179464.150}         &                    \\
      \rl{0.99}   & \cost{158034.800} & \cost{212726.200} & \cost{701300.800} & \fgiboc{212726.200}{701300.800} & \cost{1072061.800}$^{2}$               & \timem{2.970} & \fgit{2.970}{4.300} & \tard{0.281} & \costpp{1072061.800}         & \rnd{115.801}      \\
      \rl{1.00}   & \cost{160453.950} & \cost{286065.800} & \cost{539803.200} & \fgiboc{286065.800}{539803.200} & \textbf{\cost{986322.950}}       & \timem{3.007} & \fgit{3.007}{4.623} & \tard{0.204} & \textbf{\costpp{986322.950}} & \rnd{109.907}      \\
      \BILOne{}   & \cost{146835.900} & \cost{     0.000} & \cost{2349374.40} & \fgiboc{     0.000}{2349374.40} & \cost{2496210.300}               & \timem{2.796} & \fgit{2.796}{3.295} & \tard{0.867} & \costpp{2496210.300}         &                    \\
      \BILTwo{}   & \cost{143756.000} & \cost{ 34112.800} & \cost{1412752.00} & \fgiboc{ 34112.800}{1412752.00} & \cost{1590620.800}               & \timem{2.748} & \fgit{2.748}{3.380} & \tard{0.529} & \costpp{1590620.800}         &                    \\

>>>>

@@

    \begin{tabular}{crrrrrlrrrrr}

@@

      % 70-\(\Unif\) & WIPC              & FGIC              & BOC                & \fgibocName                     & SUM                        &                          & SFTT          & FGIT                & SL(\%)       & Cost.p.P                     & \(\avgrew^{\pol}\) \\
      % \midrule     &
      % \ql{0.99}    & \cost{38776.300}  & \cost{133872.800} & \cost{82673.600 }  &                                 & \cost{255322.700}          &                          & \timem{1.340} & \timem{2.558}       & \tard{0.095} &                              &                    \\
      % \rl{0.99}    & \cost{37111.000}  & \cost{113425.600} & \cost{98654.400 }  &                                 & \cost{249191.000}          &                          & \timem{1.305} & \timem{2.412}       & \tard{0.110} &                              &                    \\
      % \rl{1.00}    & \cost{38755.000}  & \cost{156444.000} & \cost{59718.400 }  &                                 & \cost{254917.400}          &                          & \timem{1.339} & \timem{2.679}       & \tard{0.068} &                              &                    \\
      % \BILOne{}    & \cost{32159.900}  & \cost{     0.000} & \cost{514558.400}  &                                 & \cost{546718.300}          &                          & \timem{1.202} & \timem{1.693}       & \tard{0.552} &                              &                    \\
      % \BILTwo{}    & \cost{32169.900}  & \cost{ 83391.200} & \cost{106219.200}  &                                 & \cost{221780.300}          &                          & \timem{1.202} & \timem{2.143}       & \tard{0.114} &                              &                    \\
      % \BILThree{}  & \cost{32239.800}  & \cost{247416.800} & \cost{21382.400 }  &                                 & \cost{301039.000}          &                          & \timem{1.204} & \timem{3.029}       & \tard{0.022} &                              &                    \\
      % \BILFour{}   & \cost{32262.600}  & \cost{428865.200} & \cost{5483.200  }  &                                 & \cost{466611.000}          &                          & \timem{1.204} & \timem{4.007}       & \tard{0.006} &                              &                    \\

@@

      70-\(\Unif\)   & WIPC              & FGIC              & BOC                & \fgibocName                     & SUM                        & \multicolumn{2}{r}{SFTT} & FGIT          & SL(\%)              & Cost.p.P     & \(\avgrew^{\pol}\)                                \\

@@

      \ql{0.99}      & \cost{38563.000}  & \cost{134703.600} & \cost{81704.800}   & \fgiboc{134703.600}{81704.800}  & \cost{254971.400}          & $^{1}$                   & \timem{1.335} & \fgit{1.335}{2.558} & \tard{0.094} & \costpp{254971.400}          &                    \\
      \rl{0.99}      & \cost{37197.750}  & \cost{113100.800} & \cost{100398.400}  & \fgiboc{113100.800}{100398.400} & \cost{250696.950}          &                          & \timem{1.307} & \fgit{1.307}{2.412} & \tard{0.111} & \costpp{250696.950}          & \rnd{35.040}       \\
      \rl{1.00}      & \cost{38659.100}  & \cost{156659.200} & \cost{59743.200}   & \fgiboc{156659.200}{59743.200}  & \cost{255061.500}          & $^{1}$                   & \timem{1.338} & \fgit{1.338}{2.678} & \tard{0.068} & \costpp{255061.500}          & \rnd{36.501}       \\
      \BILOne{}      & \cost{32056.500}  & \cost{0.000}      & \cost{512904.000}  & \fgiboc{0.000}{512904.000}      & \cost{544960.500}          &                          & \timem{1.200} & \fgit{1.200}{1.691} & \tard{0.551} & \costpp{544960.500}          &                    \\
      \BILTwo{}      & \cost{32063.850}  & \cost{83461.000}  & \cost{105009.600}  & \fgiboc{83461.000}{105009.600}  & \textbf{\cost{220534.450}} &                          & \timem{1.200} & \fgit{1.200}{2.142} & \tard{0.114} & \textbf{\costpp{220534.450}} &                    \\
      \BILThree{}    & \cost{32155.150}  & \cost{247727.000} & \cost{21680.800 }  & \fgiboc{247727.000}{21680.800 } & \cost{301562.950}          &                          & \timem{1.202} & \fgit{1.202}{3.029} & \tard{0.022} & \costpp{301562.950}          &                    \\
      \BILFour{}     & \cost{32140.550}  & \cost{429097.800} & \cost{5076.800 }   & \fgiboc{429097.800}{5076.800 }  & \cost{466315.150}          &                          & \timem{1.202} & \fgit{1.202}{4.007} & \tard{0.005} & \costpp{466315.150}          &                    \\

@@

      80-\(\Unif\)   & WIPC              & FGIC              & BOC                & \fgibocName                     & SUM                        & \multicolumn{2}{r}{SFTT} & FGIT          & SL(\%)              & Cost.p.P     & \(\avgrew^{\pol}\)                                \\

@@

      \ql{0.99}      & \cost{63095.100}  & \cost{180403.800} & \cost{121528.000}  & \fgiboc{180403.800}{121528.000} & \textbf{\cost{365026.900}} &                          & \timem{1.680} & \fgit{1.680}{3.019} & \tard{0.103} & \textbf{\costpp{365026.900}} &                    \\
      \rl{0.99}      & \cost{65310.650}  & \cost{168489.200} & \cost{148593.600}  & \fgiboc{168489.200}{148593.600} & \cost{382393.450}          &                          & \timem{1.721} & \fgit{1.721}{3.005} & \tard{0.136} & \costpp{382393.450}          & \rnd{52.918}       \\
      \rl{1.00}      & \cost{60778.500}  & \cost{234045.000} & \cost{76168.000}   & \fgiboc{234045.000}{76168.000}  & \cost{370991.500}          & $^{1}$                   & \timem{1.637} & \fgit{1.637}{3.226} & \tard{0.066} & \costpp{370991.500}          & \rnd{52.291}       \\
      \BILOne{}      & \cost{51888.650}  & \cost{0.000}      & \cost{830218.400}  & \fgiboc{0.000}{830218.400}      & \cost{882107.050}          &                          & \timem{1.474} & \fgit{1.474}{1.968} & \tard{0.672} & \costpp{882107.050}          &                    \\
      \BILTwo{}      & \cost{51998.950}  & \cost{70108.800}  & \cost{255166.400}  & \fgiboc{70108.800}{255166.400}  & \cost{377274.150}          &                          & \timem{1.476} & \fgit{1.476}{2.298} & \tard{0.206} & \costpp{377274.150}          &                    \\
      \BILThree{}    & \cost{51976.550}  & \cost{240175.000} & \cost{77822.400}   & \fgiboc{240175.000}{77822.400}  & \cost{369973.950}          & $^{1}$                   & \timem{1.475} & \fgit{1.475}{3.091} & \tard{0.060} & \costpp{369973.950}          &                    \\
      \BILFour{}     & \cost{51827.050}  & \cost{442307.600} & \cost{26711.200}   & \fgiboc{442307.600}{26711.200}  & \cost{520845.850}          &                          & \timem{1.472} & \fgit{1.472}{4.031} & \tard{0.019} & \costpp{520845.850}          &                    \\

@@

      90-\(\Unif\)   & WIPC              & FGIC              & BOC                & \fgibocName                     & SUM                        & \multicolumn{2}{r}{SFTT} & FGIT          & SL(\%)              & Cost.p.P     & \(\avgrew^{\pol}\)                                \\

@@

      \ql{0.99}      & \cost{98909.150}  & \cost{190681.000} & \cost{297333.600}  & \fgiboc{190681.000}{297333.600} & \cost{586923.750}          & $^{1}$                   & \timem{2.133} & \fgit{2.133}{3.417} & \tard{0.173} & \costpp{586923.750}          &                    \\
      \rl{0.99}      & \cost{105348.200} & \cost{263950.600} & \cost{207183.200}  & \fgiboc{263950.600}{207183.200} & \textbf{\cost{576482.000}} & $^{1}$                   & \timem{2.238} & \fgit{2.238}{3.825} & \tard{0.121} & \textbf{\costpp{576482.000}} & \rnd{79.826}       \\
      \rl{1.00}      & \cost{107873.800} & \cost{240798.800} & \cost{253865.600}  & \fgiboc{240798.800}{253865.600} & \cost{602538.200}          & $^{2}$                   & \timem{2.280} & \fgit{2.280}{3.771} & \tard{0.153} & \costpp{602538.200}          & \rnd{80.425}       \\
      \BILOne{}      & \cost{88658.100}  & \cost{0.000}      & \cost{1418529.600} & \fgiboc{0.000}{1418529.600}     & \cost{1507187.700}         &                          & \timem{1.964} & \fgit{1.964}{2.462} & \tard{0.790} & \costpp{1507187.700}         &                    \\
      \BILTwo{}      & \cost{88317.700}  & \cost{50854.400}  & \cost{646000.800}  & \fgiboc{50854.400}{646000.800}  & \cost{785172.900}          &                          & \timem{1.958} & \fgit{1.958}{2.666} & \tard{0.355} & \costpp{785172.900}          &                    \\
      \BILThree{}    & \cost{88252.450}  & \cost{207210.600} & \cost{299885.600}  & \fgiboc{207210.600}{299885.600} & \cost{595348.650}          & $^{2}$                   & \timem{1.957} & \fgit{1.957}{3.309} & \tard{0.148} & \costpp{595348.650}          &                    \\
      \BILFour{}     & \cost{87774.600}  & \cost{415178.200} & \cost{153612.800}  & \fgiboc{415178.200}{153612.800} & \cost{656565.600}          &                          & \timem{1.950} & \fgit{1.950}{4.158} & \tard{0.071} & \costpp{656565.600}          &                    \\

@@

    not significantly different from each other.}

@@

\paragraph{Medium Variability.} The results for medium variability in the system are presented in
Table~\ref{tbl:unif}, where a uniform demand interarrival time is used. We use the tuples
\(70-\Unif\), \(80-\Unif\), and \(90-\Unif\) to indicate the experimental setup of using uniform
demand interarrival times with a aimed bottleneck utilisation of \(70\%\), \(80\%\), or \(90\%\)
respectively. The results state the accumulated costs, averaged over all replications, for the work
in process (WIPC), the finished goods inventory (FGIC), the backorder costs (BOC), as well as the
sum of the finished good inventory and backorder costs (\fgibocName{}) and the sum over all three cost
centers (SUM). For a better insight in the timing performance we also provide the average shopfloor
throughput time (SFTT), i.e.\@ the average time an order spends in the system after being released
and until reaching the finished goods inventory, the finished goods inventory time (FGIT), as well
as the service level (SL). The later is given in percentage and states the percentage of orders that
were produced on time. Finally, the actual measured costs per period (Cost.p.P) and the by the
algorithm learned average reward \(\avgrew\) are stated. The tested methods are the deep Q-Learning
algorithm with discount factor \(0.99\) (\qlt{0.99}), the \ARA{} algorithm with discount factors
\(0.99\) (\rlt{0.99}) and \(1.00\) (\rlt{1.00}), as well as the backward infinite loading
technique \BIL{} with fixed lead times between \(1\) and \(4\) as indicated by the number
($\BILOne$-$\BILFour$).

For the case of medium variability with a utilisation of \(70\%\) (\(70-\Unif\)) we can see that
\(\BILTwo\) performs best in the sense of accumulated costs. The reinforcement learning algorithm
follow, where \rlt{0.99} is significantly better then the other two variants. The other \BIL{}
variants accumulate much more costs. For the timing one can see that \rlt{1.00} performs very good
with a service level of \(93.2\%\). Furthermore, the learned average reward \(\avgrew\) and actual
average reward are very similar for both \ARA{} variants. However, with \(70\%\) of utilisation the
overhead of the reinforcement learning variants are too big to be able to compete with the simple
rule based release mechanism of \(\BILTwo{}\) as for changing workload the utilisation changes
rather linearly due to the low variability in the system.

In the case of \(80-\Unif\)

@@

  \footnotesize

@@

      70-\(\Exp\) & WIPC              & FGIC              & BOC               & \hide{\fgibocName{}}                        & SUM                            &  \multicolumn{2}{r}{SFTT}          & FGIT                & SL(\%)       & Cost.p.P                     & \(\avgrew^{\pol}\) \\

@@

      \ql{0.99}   & \cost{53873.500}  & \cost{142398.800} & \cost{164427.200} & \fgiboc{142398.800}{164427.200} & \cost{360699.500}&$^{1}$          & \timem{1.585} & \fgit{1.585}{2.796} & \tard{0.162} & \costpp{360699.500}          &                    \\
      \rl{0.99}   & \cost{61419.850}  & \cost{181702.200} & \cost{115287.200} & \fgiboc{181702.200}{115287.200} & \cost{358409.250}&                & \timem{1.734} & \fgit{1.734}{3.145} & \tard{0.107} & \costpp{358409.250}          & \rnd{50.787}       \\
      \rl{1.00}   & \cost{56578.800}  & \cost{199310.000} & \cost{115714.400} & \fgiboc{199310.000}{115714.400} & \cost{371603.200}&                & \timem{1.639} & \fgit{1.639}{3.136} & \tard{0.113} & \costpp{371603.200}          & \rnd{50.575}       \\
      \BILOne{}   & \cost{48547.100}  & \cost{     0.000} & \cost{776753.600} & \fgiboc{     0.000}{776753.600} & \cost{825300.700}&                & \timem{1.479} & \fgit{1.479}{1.975} & \tard{0.663} & \costpp{825300.700}          &                    \\
      \BILTwo{}   & \cost{48618.850}  & \cost{ 66927.200} & \cost{248638.400} & \fgiboc{ 66927.200}{248638.400} & \cost{364184.450}&$^{1}$          & \timem{1.480} & \fgit{1.480}{2.312} & \tard{0.220} & \costpp{364184.450}          &                    \\
      \BILThree{} & \cost{48632.050}  & \cost{222603.200} & \cost{ 74568.800} & \fgiboc{222603.200}{ 74568.800} & \textbf{\cost{345804.050}}&       & \timem{1.481} & \fgit{1.481}{3.094} & \tard{0.063} & \textbf{\costpp{345804.050}} &                    \\
      \BILFour{}  & \cost{48514.200}  & \cost{409531.200} & \cost{ 23406.400} & \fgiboc{409531.200}{ 23406.400} & \cost{481451.800}       &         & \timem{1.478} & \fgit{1.478}{4.029} & \tard{0.019} & \costpp{481451.800}          &                    \\

@@

      80-\(\Exp\) & WIPC              & FGIC              & BOC               & \hide{\fgibocName}                        & SUM                             &\multicolumn{2}{r}{SFTT}          & FGIT                & SL(\%)       & Cost.p.P                     & \(\avgrew^{\pol}\) \\

@@

      \ql{0.99}   & \cost{87706.700}  & \cost{227485.400} & \cost{225150.400} & \fgiboc{227485.400}{225150.400} & \cost{540342.500}&$^{1}$          & \timem{2.043} & \fgit{2.043}{3.541} & \tard{0.166} & \costpp{540342.500}          &                    \\
      \rl{0.99}   & \cost{89838.950}  & \cost{253476.000} & \cost{185687.200} & \fgiboc{253476.000}{185687.200} & \cost{529002.150}&$^{1,2}$        & \timem{2.078} & \fgit{2.078}{3.689} & \tard{0.124} & \costpp{529002.150}          & \rnd{70.527}       \\
      \rl{1.00}   & \cost{87171.500}  & \cost{242915.600} & \cost{198456.000} & \fgiboc{242915.600}{198456.000} & \cost{528543.100}&$^{2,3}$        & \timem{2.034} & \fgit{2.034}{3.599} & \tard{0.134} & \costpp{528543.100}          & \rnd{72.944}       \\
      \BILOne{}   & \cost{78731.850}  & \cost{     0.000} & \cost{1259709.60} & \fgiboc{     0.000}{1259709.60} & \cost{1338441.45}&                & \timem{1.884} & \fgit{1.884}{2.382} & \tard{0.771} & \costpp{1338441.450}         &                    \\
      \BILTwo{}   & \cost{78203.150}  & \cost{ 52303.200} & \cost{548736.000} & \fgiboc{ 52303.200}{548736.000} & \cost{679242.350}&                & \timem{1.875} & \fgit{1.875}{2.602} & \tard{0.350} & \costpp{679242.350}          &                    \\
      \BILThree{} & \cost{79029.850}  & \cost{200273.200} & \cost{242100.800} & \fgiboc{200273.200}{242100.800} & \textbf{\cost{521403.850}}&$^{3}$ & \timem{1.890} & \fgit{1.890}{3.265} & \tard{0.142} & \textbf{\costpp{521403.850}} &                    \\
      \BILFour{}  & \cost{79384.750}  & \cost{395493.000} & \cost{116943.200} & \fgiboc{395493.000}{116943.200} & \cost{591820.950} &               & \timem{1.896} & \fgit{1.896}{4.128} & \tard{0.062} & \costpp{591820.950}          &                    \\

@@

      90-\(\Exp\) & WIPC              & FGIC              & BOC               & \hide{\fgibocName}                        & SUM                              & \multicolumn{2}{r}{SFTT}          & FGIT                & SL(\%)       & Cost.p.P                     & \(\avgrew^{\pol}\) \\

@@

      \ql{0.99}   & \cost{168655.950} & \cost{222145.800} & \cost{788662.400} & \fgiboc{222145.800}{788662.400} & \cost{1179464.150}&$^{1}$               & \timem{3.134} & \fgit{3.134}{4.501} & \tard{0.285} & \costpp{1179464.150}         &                    \\
      \rl{0.99}   & \cost{158034.800} & \cost{212726.200} & \cost{701300.800} & \fgiboc{212726.200}{701300.800} & \cost{1072061.800}&$^{2}$               & \timem{2.970} & \fgit{2.970}{4.300} & \tard{0.281} & \costpp{1072061.800}         & \rnd{115.801}      \\
      \rl{1.00}   & \cost{160453.950} & \cost{286065.800} & \cost{539803.200} & \fgiboc{286065.800}{539803.200} & \textbf{\cost{986322.950}}&       & \timem{3.007} & \fgit{3.007}{4.623} & \tard{0.204} & \textbf{\costpp{986322.950}} & \rnd{109.907}      \\
      \BILOne{}   & \cost{146835.900} & \cost{     0.000} & \cost{2349374.40} & \fgiboc{     0.000}{2349374.40} & \cost{2496210.300}&               & \timem{2.796} & \fgit{2.796}{3.295} & \tard{0.867} & \costpp{2496210.300}         &                    \\
      \BILTwo{}   & \cost{143756.000} & \cost{ 34112.800} & \cost{1412752.00} & \fgiboc{ 34112.800}{1412752.00} & \cost{1590620.800}&               & \timem{2.748} & \fgit{2.748}{3.380} & \tard{0.529} & \costpp{1590620.800}         &                    \\
